### 2019-10-28 Manuscript/Supplementary_Information/Supplementary_Information.tex
Updates from Overleaf

\begin{flushleft}
{\Large \textbf{Supplementary Information for ``Emergence of the SE Asian islands as a driver for Neogene cooling''}}

@@

\section*{SE Asian Islands Scenarios}

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/SEAI_fracs.jpg}
    \caption{0.5\degrees $\times$ 0.5\degrees lithologic maps of the SE Asian islands (SEAI) used to force GEOCLIM. Only the 15~Ma scenarios are shown here, but the 10 and 5~Ma scenarios would be similar, using the 10 and 5~Ma shorelines shown in Figure 1 of the main text instead. Each column represents a tested scenario. Each row represents a lithologic category. Solid black lines show present-day shorelines.}
    \label{fig:SEAI_fracs}
\end{figure}

>>>>

\begin{flushleft}
{\Large \textbf{Supplementary Information for ``Emergence of the Southeast Asian islands as a driver for Neogene cooling''}}

@@

\section*{Southeast Asian Islands Scenarios}

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\textwidth]{Manuscript/Figures/SEAI_fracs.jpg}
    \caption{0.5\degrees $\times$ 0.5\degrees lithologic maps of the Southeast Asian islands (SEAI) used to force GEOCLIM. Only the 15~Ma scenarios are shown here, but the 10 and 5~Ma scenarios would be similar, using the 10 and 5~Ma shorelines shown in Figure 1 of the main text instead. Each column represents a tested scenario. Each row represents a lithologic category. Solid black lines show present-day shorelines.}
    \label{fig:SEAI_fracs}
\end{figure}
